% !TEX TS-program = XeLaTeX
%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kieran Healy <kjhealy@gmail.com>
%%% Most recent version is at http://kjhealy.github.com/kjh-vita
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip,
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or
%%% remove these as needed.
%%%------------------------------------------------------------------------
\documentclass[11pt,article,oneside]{memoir}
\usepackage{org-preamble-xelatex}
\usepackage{fontspec}
\usepackage{url}

% \usepackage[none]{hyphenat} % suppress words breaking across lines

\usepackage{fontawesome5}

\addbibresource{/Users/timothyelder/Documents/bibs/socbib-pandoc.bib}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Timothy B. Elder}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{Geisel School of Medicine}
\def\myinstitution{Dartmouth College}
\def\mydepartmentweb{https://geiselmed.dartmouth.edu/tdi/}
\def\mydepartment{The Dartmouth Institute}
\def\myemail{timothy.b.elder@dartmouth.edu}
\def\myphone{(740) 913-1219}
\def\myweb{timothyelder.com}
\def\myversion{}
\def\myrevision{}

\def\myblue{018DE9}
\def\dartmouthgreen{00693e}


\def\myauthor{Timothy Elder}
\date{} % not used (revision control instead)
\def\mykeywords{Timothy, Elder, Timothy Elder, Vita, CV, Resume, Sociology}

%%%------------------------------------------------------------------------
%%% Git version tracking
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
\input{vc}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

\raggedright

\setromanfont[Mapping={tex-text},
	Numbers={OldStyle},
	Ligatures={Common}]{Dartmouth Ruzicka}

\setsansfont[Mapping=tex-text,
	Ligatures={Common},
	Colour=\dartmouthgreen]{National 2}

\setmonofont[Mapping=tex-text,Scale=0.72]{Iosevka}

\newfontface\scheader[SmallCapsFont={Dartmouth Ruzicka},SmallCapsFeatures={Letters=SmallCaps}]{Dartmouth Ruzicka}

\newfontface\addressblock[Mapping={tex-text},
	Numbers={OldStyle},
	Ligatures={Common}]{Dartmouth Ruzicka}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Presentations Command

\newcommand{\present}[6]{\ind ``#1'', \emph{#2}, #3. #4, #5. #6. \vspace{0.10in}}

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~}

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the vc
% package---see docs for vc package for details. Comment out this line
% if you're not using vc, and also remove the \input{vc} line above.
% \pagestyle{kjh}
\thispagestyle{kjhgit}


%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize
 \href{\mydepartmentweb}{\mydepartment} \\ \myaffiliation \\ \myinstitution \\ \vspace{-0.05in} Lebanon, \textsc{NH} 03766}

\end{minipage}
\hfill
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.5in}
  \flushright \footnotesize  \addressblock
  {\scriptsize  \texttt{\href{https://\myweb}{\myweb}}} \faIcon{globe-americas} \\
  {\scriptsize  \texttt{\href{https://github.com/timothyelder}{github.com/timothyelder} \faIcon{github}} \\
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \faIcon{envelope}} \\
  {\scriptsize  \texttt{\href{https://orcid.org/0000-0003-4164-1130}{0000-0003-4164-1130}} \faIcon{orcid}}}
\end{minipage}

\bigskip

%%%%%%%%%%
%% Name %%
%%%%%%%%%%
\noindent{\LARGE\scheader \textsc{TIMOTHY B. ELDER}}
\reversemarginpar

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%
%% Academic Positions %%
%%%%%%%%%%%%%%%%%%%%%%%%
\marginhead{\sffamily {{\vskip -1pt} academic \newline positions}}

\ind Postdoctoral Research Associate, The Dartmouth Institute for Health Policy \& Clinical Practice, Dartmouth College, 2024-2026

\vspace{20pt}

%%%%%%%%%%%%%%%
%% Education %%
%%%%%%%%%%%%%%%
\marginhead{\sffamily {{\vskip -6pt} education}}

\ind PhD, Sociology, University of Chicago, \emph{2024}.

\ind \hspace{0.35in} \footnotesize Dissertation: \emph{Winning at a Losing Game - Divergent Ontologies and Shared Practices in Medicine}. \normalsize \vskip 0.23em

\ind MA, Sociology, University of Chicago, 2018.

\ind BA, \emph{Cum Laude}, Philosophy and Sociology, Kent State University, 2016. \vspace{0.1in}

\bigskip

%%%%%%%%%%%
%% Books %%
%%%%%%%%%%%
\marginhead{\sffamily {{\vskip -6pt}books}}

\ind \textit{Winning at a Losing Game: Medicine's Challenge in Caring for the Dying}\\
\strut\hspace{0.4in} \footnotesize \textbf{In Preparation}\normalsize \\\vspace{0.1in}

\ind \textit{Introduction to PlainText for Research \& Writing: Open Workflows for Reproducible Scholarship}\\
\strut\hspace{0.4in} \footnotesize \textbf{In Preparation}\\\vspace{0.1in}

\medskip

%%%%%%%%%%%%
%% Papers %%
%%%%%%%%%%%%
\marginhead{\sffamily {{\vskip -6pt}papers}}

\normalsize

\ind \fullcite{elder_status_2025} \\\vspace{0.1in}

\ind Timothy B. Elder ``The Operation was Successful and the Patient Died: Good Practice and Bad Results in the Care of the Dying'' \\
	\strut\hspace{0.4in} \footnotesize \textbf{Forthcoming} at \textit{Qualitative Sociology} \normalsize \\\vspace{0.1in}

\ind Timothy B. Elder ``Ambiguity at the End of Life: The Breakdown of Clinical Heuristics in Serious Illness'' \\
	\strut\hspace{0.4in} \footnotesize \textbf{Under Review} at \textit{Sociology of Health and Illness} \normalsize \\\vspace{0.1in}

\medskip

%%%%%%%%%%%%%%%%%%%%
%% Working Papers %%
%%%%%%%%%%%%%%%%%%%%
\marginhead{\sffamily working\newline papers}

\ind Timothy B. Elder ``Discourse of Data and Talk of Values: Integrating Patient-Clinician Decision-Making in End-of-Life Care'' \\
	% \strut\hspace{0.4in} \footnotesize \textbf{Under Review} at \textit{Sociological Forum} \normalsize \\

\newpage

%%%%%%%%%%%%%%
%% Teaching %%
%%%%%%%%%%%%%%
\marginhead{\sffamily {\vskip 0.6em} teaching}
\medskip

\noindent\emph{Dartmouth College \vspace{0.01in}}

\ind Lecturer, \underline{Medical Sociology}. Winter 2026.\vspace{0.05in}

\medskip
\noindent\emph{University of Chicago \vspace{0.01in}}

\ind Teaching Assistant, \underline{Invitation to Sociology}. Spring 2022.

\ind Teaching Assistant, \underline{Maverick Markets}. Spring 2020.

\ind Teaching Assistant, \underline{Social, Structure, and Change}. Winter 2020.

\ind Teaching Assistant, \underline{Urban Policy Analysis}. Autumn 2019.

\ind Teaching Assistant, \underline{Sociology of Human Sexuality}. Spring 2020.

\ind Teaching Intern, \underline{Power, Identity, and Resistance}. Autumn and Winter 2018-2019.

%%%%%%%%%%%%%%
%% Research %%
%%%%%%%%%%%%%%
\marginhead{\sffamily {\vskip 0.35em} research}
\medskip
\noindent\emph{University of Chicago \vspace{0.01in}}

\ind Research Assistant, Ensago-Networks Project, Summer and Autumn 2021. \vspace{0.05in}

\ind Course Development, \underline{Invitation to Sociology}, 2018-2019. \vspace{0.05in}

\smallskip
\noindent\emph{Kent State University \vspace{0.01in}}

\ind Research Assistant, Group Processes EEG Laboratory, 2015-2016. \vspace{0.1in}

\normalsize

\bigskip

%%%%%%%%%%%%%%%%%%%
%% Invited Talks %%
%%%%%%%%%%%%%%%%%%%
\marginhead{\sffamily invited\newline talks}
\medskip

\present{From Talk to Action: The Role of Interactional Style in Tumor Board Decision-Making}{University of Vermont}{2025}{Burlington}{VT}{Vermont Conversation Lab}

\present{The Operation Was Successful and the Patient Died: Success and Failure in the Care of the Dying}{University of Chicago}{2025}{Chicago}{IL}{Aging Crossroads Lecture Series, Department of Medicine, Section of Geriatrics and Palliative Care}

\present{The Operation Was Successful and the Patient Died: Success and Failure in the Care of the Dying}{Northwestern University}{2024}{Chicago}{IL}{Department of Medicine, Section of Palliative Care}

\bigskip

%%%%%%%%%%%%%%%%%%%
%% Presentations %%
%%%%%%%%%%%%%%%%%%%
\marginhead{\sffamily presentations}
\medskip

\present{The Operation was Successful and the Patient Died: Success in the Care of the Dying}{ASA Annual Meeting}{2024}{Montreal}{CA}{Regular Session Medical Sociology}

\present{The Ratlines --- Clandestine Networks and Nazi Fugitives at the End of the Second World War}{ASA Annual Meeting}{2023}{Philadelphia}{PA}{Regular Session Historical Sociology}

\present{Intra-Professional Collaboration in the Hospital}{Chicago Ethnography Conference, Loyola University}{2023}{Chicago}{IL}{}

\present{Intra-Professional Collaboration in Acute Hospital Settings}{Midwest Sociological Society Annual Conference}{2023}{Minneapolis}{MN}{}

\present{Intra-Professional Collaboration in Medicine: Applying Ecological Concepts to Hospice and Palliative Medicine}{Eastern Sociological Society Annual Conference}{2023}{Baltimore}{MD}{}

\present{Status and Subfield: The Distribution of Sociological Specializations across Departments}{ASA Annual Meeting}{2022}{Los Angeles}{CA}{Regular Session History of Sociology and Social Thought}

% \present{An Empirical Investigation of Privacy: The Impact of Multiple Levels of Trust}{ASA Annual Meeting}{2015}{Chicago}{IL}{Roundtable}

% \present{An Empirical Perspective on Altman's Theory of Privacy}{North Central Sociological Association}{2015}{Cleveland}{OH}{}

\normalsize

%%%%%%%%%%%%%
%% Service %%
%%%%%%%%%%%%%
\medskip
\marginhead{\sffamily {\vskip 0.35em} service}
\medskip

\ind Creator and Coordinator, \texttt{PlainText Working Group}. Winter and Spring 2023.

\ind Book Review Board, \emph{American Journal of Sociology}, 2021-2022.

\ind Manuscript Board, \emph{American Journal of Sociology}, 2018-2019.

\ind Student Coordinator, \emph{Social Theory and Evidence Workshop}, 2018-2019.

\ind Student Coordinator, \emph{UChicago Sociology Colloquium}, 2018-2019.

\ind Co-Chair, \emph{Society for Social Research}, 2018-2019.

\ind Reviewer, \emph{American Journal of Sociology, Sexuality \& Culture, Journal of Public Health and Community Medicine}

%% Professional Membership
\medskip
\marginhead{\sffamily {\vskip 0.35em} professional \newline membership}
\medskip

\ind \emph{Eastern Sociological Society}. 2022-Present.

\ind \emph{Midwest Sociological Society}. 2019-2022.

\ind \emph{American Sociological Association}. 2015-Present.

\bigskip
\marginhead{\sffamily {\vskip 0.35em} programming languages}

\medskip

\ind \texttt{python} \hspace{0.4in}  \texttt{R} \hspace{0.4in} \texttt{git} \hspace{0.4in} \LaTeX

%% Research Interests
\medskip
\marginhead{\sffamily {\vskip 0.75cm} research \newline interests}
\bigskip

\vskip 25pt

\begin{minipage}{\textwidth}
	\begin{minipage}{0.48\textwidth}
	Sociology of Medicine \\ Computational Methods \\ Organizations
	\end{minipage}\hfill
	\begin{minipage}{0.52\textwidth}
	Qualitative Methods \\ Health Services Research \\ Death and Dying
	\end{minipage}%
\end{minipage}

%% References
\bigskip
\marginhead{\sffamily {\vskip 0.35em} references}
\bigskip

\begin{minipage}[t]{0.30\textwidth}
	John Levi Martin \\
	Professor of Sociology \\
	University of Chicago \\
	1126 East 59th St. \\
	Chicago, IL 60637 \\
	\texttt{\href{mailto:jlmartin@uchicago.edu}{jlmartin@uchicago.edu}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.30\textwidth}
	Jenny Trinitapoli \\
	Professor of Sociology \\
	University of Chicago \\
	1126 East 59th St. \\
	Chicago, IL 60637 \\
	\texttt{\href{mailto:jennytrini@uchicago.edu}{jennytrini@uchicago.edu}} \\
\end{minipage}
\hfill
\begin{minipage}[t]{0.30\textwidth}
	Amber Barnato \\
	Professor of Medicine \\
	Dartmouth College \\
	1 Medical Center Drive \\
	Lebanon, NH 03766 \\
	\texttt{\href{mailto:amber.barnato@dartmouth.edu}{amber.barnato@dartmouth.edu}} \\
\end{minipage}

% \bigskip


% \hfill
% \begin{minipage}[t]{0.48\textwidth}
% 	Genevra Murray \\
% 	Asst. Professor of Public Health \\
% 	New York University\\
% 	708 Broadway\\
% 	New York, NY, 10003\\
% 	\texttt{\href{mailto:genevra.murray@nyu.edu}{genevra.murray@nyu.edu}}
% \end{minipage}

\end{document}
